Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-11-23 EJP396.tex
add EJP396.tex

\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
%DELETED
%\usepackage{stackrel}
%END DELETED
\usepackage{mathrsfs}
\usepackage{hyperref}

@@

\TITLE{
	Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes 
\thanks{
	%Y-X Ren's research  is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF. 
	Yan-Xia Ren's research is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF. 
	%
	\newline
	Renming Song's research is partially supported by the Simons Foundation 
	%(\#429343, Renming Song)
	(\#429343, Renming Song).
}} 
% \thanks is optional. Insert line breaks with \\

@@

%\AUTHORS{%
%	Y.-X. Ren
%	\footnote{Peking University, Beijing, P. R. China, 100871.
%		\EMAIL{yxren@math.pku.edu.cn}}
%	\and 
%	Renming Song
%	\footnote{University of Illinois at Urbana-Champaign, Urbana, IL, USA, 61801. 
%		\EMAIL{rsong@illinois.edu}}
%	\and
%	Zhenyao Sun
%	\footnote{ Wuhan University, Hubei, P. R. China, 430072.
%		\EMAIL{zhenyao.sun@gmail.com}}
%	\and
%	Jianjie Zhao
%	\footnote{ Peking University, Beijing, P. R. China, 100871.
%		\EMAIL{zhaojianjie@pku.edu.cn}}
%}

\AUTHORS{%
	Yan-Xia Ren
\footnote{
	Peking University, Beijing 100871, P. R. China
	\EMAIL{yxren@math.pku.edu.cn, zhenyao.sun@gmail.com, zhaojianjie@pku.edu.cn}
}
\and 
	Renming Song
\footnote{
	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA. 
	\EMAIL{rsong@illinois.edu}
}
\and
	Zhenyao Sun
\footnote{
	Wuhan University, Wuhan, Hubei 430072, P. R. China.
	\EMAIL{zhenyao.sun@gmail.com}
}
\footnote{
	Technion Israel Instituteof Technology, Haifa 32000, Israel.
	\EMAIL{zhenyao.sun@gmail.com}
}
\footnotemark[2]
\and
	Jianjie Zhao
\footnotemark[2]
}
%AUTHORS
%% Type \and between all consecutive authors (not only before the last author).
%% Note: you may use \BEMAIL to force a line break before e-mail display.

%% Here is a compact example with two authors with same affiliation
%% \AUTHORS{%
%%  Michael~First\footnote{Some University. \EMAIL{mf,js@uni.edu}
%%  \and 
%%  John~Second\footnotemark[2]}%AUTHORS
%% Note: The \footnotemark is the footnote number that you wish to reuse. Here
%% it is [2] (we took into account the footnote generated by \thanks in title).

@@

% \KEYWORDS{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime} 
\KEYWORDS{
	Superprocesses; 
	Ornstein-Uhlenbeck processes; 
	Stable distribution; 
	Central limit theorem; 
	% Law of large numbers; 
	Law of large number;
	Branching rate regime} 
% Separate items with ;

@@

\ABSTRACT{ 
	In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$ whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
	and whose branching mechanism $\psi$ satisfies Grey's condition and 
	%some perturbation condition 
	a perturbation condition 
	which guarantees that, when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
	Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for $(X_t(f) )_{t\geq 0}$, where the function $f$ is assumed to be of polynomial growth.
	A phase transition arises  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes 
	% corresponding 
	corresponding to
	the branching rate being relatively small, large or critical at a balanced value.
}

@@

\subsection{Motivation}
\label{subsec:M}
	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
% \begin{align}
\[
	Lf(x)
	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x), 
	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
% \end{align}
\]
	where $\sigma > 0$ and $b > 0$ are constants.
	Let $\psi$ be a function on $\mathbb R_+$ of the form
% \begin{align}
\begin{equation}
\label{eq: honogeneou branching mechanism}
	\psi(z)
	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy), 
	\quad  z \in \mathbb R_+,
% \end{align}
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
	$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
	Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
	We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.$
	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on  $(\Omega, \mathscr{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
%\begin{align}
\begin{equation}
\label{eq: def of V_t}
	\mathbb{P}_{\mu}[e^{-X_t(f)}]
	= e^{-\mu(V_tf)}, 
	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
% \end{align}
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
% \begin{align}
\[
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
	= \Pi_x [f(\xi_t)], 
	\quad x\in \mathbb R^d, t\geq 0.
% \end{align}
\]	
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.

	Recently, there have been quite a few papers on laws of large numbers for superdiffusions.
	In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
	The strong law of large numbers for superprocesses 
	%was first 
	were first 
	studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
	For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

@@

	In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
	Our key assumption is that $\psi$ satisfies Grey's condition 
	and some perturbation condition 
	% and a perturbation condition 
	which guarantees that, when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
	Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that $(X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
	Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.

	There are many papers on CLTs for branching processes, branching diffusions 
	%and superprocesses under the second moment condition.
	and superprocesses, under the second moment condition.
	See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
	Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved 
	%in \cite{AdamczakMilos2015CLT} and some 
	in \cite{AdamczakMilos2015CLT}, and some 
	spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
	These two papers made connections between CLTs and branching rate regimes.
	Some spatial CLTs  for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
	Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
	Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
	The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

	There are also many limit theorems for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
	Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
	Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes, under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
	Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
	They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
	We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of 
	%branching random walks and \cite{RenSongSun2018Limit} considered 
	branching random walks, and \cite{RenSongSun2018Limit} considered 
	the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching mechanism.

@@

\begin{assumption}
\label{asp: branching mechanism}
	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
%  \begin{align}
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
%  \end{align}
\end{equation}  
	for some $\delta > 0$.
\end{assumption}

@@

	The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
	It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
%\begin{align}
\begin{equation}
\label{invariantdensity}
	\varphi(x)dx
	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
%\end{align}
\end{equation}
	which is a   symmetric multivariate Gaussian distribution.
	Let $L^2(\varphi)$ be the Hilbert space with inner product
% \begin{align}
\[ 
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
%\end{align}
\]
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
	The \emph{Hermite polynomials} are defined by
%\begin{align}
\[
	H_p(x)
	:=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2), 
	\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
%\end{align}
\]
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
	For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
%\begin{align}
\begin{equation}
\label{eigenfunction}
	\phi_p(x)
  	:= \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big), 
  	\quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
%\end{align}
\end{equation}
	In other words,
\(
  	P_t\phi_p(x)
  	= e^{-b|p|t}\phi_p(x)
\)
	for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
	Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
	Thus for each $f\in L^2(\varphi)$, we have
%\begin{align}
\begin{equation}
\label{semicomp1}
  	f
  	= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
  	\quad \text{in~} L^2(\varphi).
% \end{align}
\end{equation}
	For each function $f\in L^2(\varphi)$, define \emph{the order of $f$} as
\[
  	\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\]
	which is the lowest non-zero frequency in the eigen-expansion \eqref{semicomp1}.
	Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is 
	%non-constant, then $\kappa_f<\infty$.
	non-zero, then $\kappa_f<\infty$.
	In particular, the order of any constant non-zero function is zero.

@@

	At this point, we should mention that the theorem above does not cover all $f\in \mathcal P$.
	Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
	Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$. 
	For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ 
	%maybe non-trivial.
	maybe non-zero.
	In this case, we do not have a CLT yet.
	We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. If this is valid, we can get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
	This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
	We leave the question of independence of the limit stable random variables to a future project.

>>>>

\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
\usepackage{hyperref}

@@

\TITLE{
	Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes
\thanks{
	Yan-Xia Ren's research is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.
\newline
	Renming Song's research is partially supported by the Simons Foundation
	(\#429343, Renming Song).
\newline
	Jianjie Zhao is the corresponding author.
}}
% \thanks is optional. Insert line breaks with \\

@@

\AUTHORS{%
	Yan-Xia Ren
\footnote{
Peking University, Beijing 100871, P. R. China.
\EMAIL{yxren@math.pku.edu.cn,  zhaojianjie@pku.edu.cn}
}
\and
	Renming Song
\footnote{
	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA.
	\EMAIL{rsong@illinois.edu}
}
\and
	Zhenyao Sun
\footnote{
	Wuhan University, Wuhan, Hubei 430072, P. R. China.
	\EMAIL{zhenyao.sun@gmail.com}
}
\footnote{
	Technion Israel Instituteof Technology, Haifa 32000, Israel.
	\EMAIL{zhenyao.sun@gmail.com}
}
\and
	Jianjie Zhao
\footnotemark[2]
}
%AUTHORS
%% Type \and between all consecutive authors (not only before the last author).
%% Note: you may use \BEMAIL to force a line break before e-mail display.

%% Here is a compact example with two authors with same affiliation
% \AUTHORS{%
%%  Michael~First\footnote{Some University. \EMAIL{mf,js@uni.edu}
%%  \and
%%  John~Second\footnotemark[2]}%AUTHORS
%% Note: The \footnotemark is the footnote number that you wish to reuse. Here
%% it is [2] (we took into account the footnote generated by \thanks in title).

@@

\KEYWORDS{
	Superprocesses;
	Ornstein-Uhlenbeck processes;
	Stable distribution;
	Central limit theorem;
Law of large numbers;
	Branching rate regime}
% Separate items with ;

@@

\ABSTRACT{
	In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$ whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
	and whose branching mechanism $\psi$ satisfies Grey's condition and
	a perturbation condition
	which guarantees that, when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
	Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for $(X_t(f) )_{t\geq 0}$, where the function $f$ is assumed to be of polynomial growth.
	A phase transition arises  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes
	corresponding to
	the branching rate being relatively small, large or critical at a balanced value.
}

@@

\subsection{Motivation}
\label{subsec:M}
	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\[
	Lf(x)
	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\]
	where $\sigma > 0$ and $b > 0$ are constants.
	Let $\psi$ be a function on $\mathbb R_+$ of the form
\begin{equation}
\label{eq: honogeneou branching mechanism}
	\psi(z)
	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy),
	\quad  z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
	$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
	Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
	We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.$
	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on  $(\Omega, \mathscr{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{equation}
\label{eq: def of V_t}
	\mathbb{P}_{\mu}[e^{-X_t(f)}]
	= e^{-\mu(V_tf)},
	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\[
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
	= \Pi_x [f(\xi_t)],
	\quad x\in \mathbb R^d, t\geq 0.
\]	
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.

	Recently, there have been quite a few papers on laws of large numbers for superdiffusions.
	In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
	The strong law of large numbers for superprocesses  was first
	studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
	For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

@@

	In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
	Our key assumption is that $\psi$ satisfies Grey's condition
	and some perturbation condition
	which guarantees that, when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
	Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that $(X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
	Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.

	There are many papers on CLTs for branching processes, branching diffusions
	and superprocesses, under the second moment condition.
	See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
	Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved
	in \cite{AdamczakMilos2015CLT}, and some
	spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
	These two papers made connections between CLTs and branching rate regimes.
	Some spatial CLTs  for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
	Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
	Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
    Functional versions of the CLTs were established in \cite{Janson2004Functional}
	for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

There are also many limit theorems for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
 Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
	Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes, under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
	Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
	They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
	We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of
	branching random walks, and \cite{RenSongSun2018Limit} considered
	the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching mechanism.

@@

\begin{assumption}
\label{asp: branching mechanism}
	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
\end{equation}
	for some $\delta > 0$.
\end{assumption}

@@

	The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
	It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
\begin{equation}
\label{invariantdensity}
	\varphi(x)dx
	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
\end{equation}
	which is a   symmetric multivariate Gaussian distribution.
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\[
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\]
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
	The \emph{Hermite polynomials} are defined by
\[
	H_p(x)
	:=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2),
	\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
\]
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
	For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
\begin{equation}
\label{eigenfunction}
	\phi_p(x)
  	:= \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
  	\quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
	In other words,
\(
  	P_t\phi_p(x)
  	= e^{-b|p|t}\phi_p(x)
\)
	for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
	Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
	Thus for each $f\in L^2(\varphi)$, we have
\begin{equation}
\label{semicomp1}
  	f
  	= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
  	\quad \text{in~} L^2(\varphi).
\end{equation}
	For each function $f\in L^2(\varphi)$, define \emph{the order of $f$} as
\[
  	\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\]
	which is the lowest non-zero frequency in the eigen-expansion \eqref{semicomp1}.
	Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is
	non-zero, then $\kappa_f<\infty$.
    In particular, the order of any non-zero constant function is zero.

@@

	At this point, we should mention that the theorem above does not cover all $f\in \mathcal P$.
	Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
	Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$.
	For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$
	maybe non-zero.
	In this case, we do not have a CLT yet.
	We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. If this is valid, we can get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
	This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
	We leave the question of the independence of the limit stable random variables to a future project.

	We now give some intuitive explanation of the branching rate regimes and the  phase transition.
	Similar explanation has been given in the context of branching-OU processes, see \cite{MarksMilos2018CLT}.
	First we mention that a super-OU process arises as the
	``high intensity'' limit of a sequence of branching-OU processes,
	see \cite{Li2011Measure-valued} for example. A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
	The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
	The coarsening effect corresponds to the increase of the spatial inequality, and is a consequence of the branching: simply an area with more particles will produce more offspring.
	The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU ``particle'' will ``forget'' its initial position exponentially fast.
